%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Philipp}{Bartsch}{ \urlstyle{same} \href{mailto:social@tastybug.com}{social@tastybug.com} | 
\href{tel:+4915142853342}{+49 1514 2853342 } |
LinkedIn://  \href{https://www.linkedin.com/in/tastybug}{\custombold{tastybug}} |  
Github:// \href{https://github.com/tastybug}{\custombold{tastybug}} \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Business Computing (B.Sc.)} 
\descript{HTW Berlin, 2008 - 2011}
\location{ Cum. GPA: 3.3 / 4.0 }
\sectionsep
\subsection{IT Specialist for} 
\subsection{Application Development} 
\descript{ITW Berlin, 2000 - 2003}
\location{ Dual Vocational Training}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/tastybug}{\custombold{tastybug}} \\
LinkedIn://  \href{https://www.linkedin.com/in/tastybug}{\custombold{tastybug}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Expertise
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Expertise}
\subsection{Development}
Backend Development \\
Frontend Development \\
Android Development \\
\sectionsep

\subsection{DevOps / Testing}
Test Automation \\
Testing Strategies \\
Build Automation \\
Continuous Deployment \\
Continuous Integration \\
\sectionsep

\subsection{methodology}
Clean Code Advocate \\
Domain Driven Design \\
Fast Feedback Loops \\
Mentoring and Pairing \\
Lean / Agile Approach \\
{\footnotesize \textit{\textbf{(Product Exploration Phase) }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Toolbox}
\location{Main Languages}
Java (JVM\&Android) \textbullet{} Groovy \textbullet{} Python 
\textbullet{} Typescript \textbullet{} SQL-92+\\
\location{Main Frameworks}
Spring \textbullet{} Spring Boot \textbullet{} Dropwizard \textbullet{} Vertx\\
\location{Testing}
Spock \textbullet{} Selenium \textbullet{} Mockito \textbullet{} JMeter\\
\location{Main Tools}
Jenkins \textbullet{} Teamcity \textbullet{} Jira \textbullet{} Trello
\textbullet{} Uservoice \textbullet{} Subversion \textbullet{} Git  \textbullet{} Nagios \textbullet{} Maven
\textbullet{} Gradle \textbullet{} Docker \textbullet{} Puppet \textbullet{} Kafka\\
\location{Operating Systems}
Debian \textbullet{} RedHat/CentOS \textbullet{} MacOS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.64\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RECENT PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Recent Projects}

\runsubsection{Senior Software Engineer}
\descript{| eBay Classifieds Group }
\location{ ongoing since June 2018 | Dreilinden, DE}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Green field international multi-tenant vehicle sale platform ("Motors Vertical")
\item Integration of massive horizontal classifieds like \href{https://www.kijiji.ca}{\custombold{Kijiji Canada}}, \href{https://www.gumtree.com.au}{\custombold{Gumtree Australia}}
\item Reformation of an inherited legacy domain model using DDD techniques
\item Mentoring of Junior Developers
\end{tightemize}
\sectionsep

\runsubsection{Senior Software Engineer}
\descript{| Deutsche Post AG (Freelance) }
\location{April  – June 2018 | Berlin, DE}
\begin{tightemize}\item Lowered operational and development costs anticipating upcoming projects by optimizing business processes and removal of legacy services.
\end{tightemize}
\sectionsep

\runsubsection{Senior DevOps Engineer}
\descript{| Deutsche Post AG (Freelance) }
\location{January 2014 – Feb 2018 | Berlin, DE}
\begin{tightemize}
\item Helped shaping a massive microservice platform, serving millions of customers.
\item Migration of critical path legacy monoliths into scalable microservices.
\item Greenfield development of full stack microservices using various techstacks.
\item Increased release frequency with improvements to the release process.
\item Introduction of Domain Driven Design into the development process.
\item Introduction of robust test automation allowing for Continuous Deployment.
\item Advocacy of systematic knowledge sharing using various techniques like mentoring, pairing, mob programming and DDD`s ubiquitous language.
\end{tightemize}
\sectionsep

\runsubsection{Co-Founder, Android Developer}
\descript{| EarlyNerds GbR }
\location{March 2013  – February 2016 | Berlin, DE}
\begin{tightemize}
\item Creation and distribution of a productivity tool for teachers.
\item Lean development of Android \& Windows Mobile apps, self distributed.
\item Established tight feedback loops with customers, leading to outstanding customer retention and user driven development.
\item Achieved leadership by market share on Windows, top 3 spot by market share on Android in Germany in our niche.
\end{tightemize}
\sectionsep

\runsubsection{Continuous Delivery Consultant}
\descript{| Freelance }
\location{October 2011  – November 2013 | Europe}
\begin{tightemize}
\item Technical consulting regarding software test automation for mobile apps.
\item Introduction of Continuous Integration \& Continuous Delivery into various backend and mobile projects.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Side Projects}

\runsubsection{Open Source Android App Development}
\descript{| Pocket Log}
\location{November 2015 – Present }
Creator and maintainer of a native Android app that offers revision-safe time tracking for Contracts and Freelancers, see \href{https://github.com/tastybug/timetracker}{\custombold{Github}} and \href{https://play.google.com/store/apps/details?id=com.tastybug.timetracker}{\custombold{App Store Presence}}
\sectionsep

\runsubsection{Plugin-Maintainer / Open Source Dev}
\descript{| Jenkins Project}
\location{2012 – 2015 }
Maintainer of the Jenkins libvirt slave plugin, see \href{https://wiki.jenkins.io/display/JENKINS/Libvirt+Slaves+Plugin}{\custombold{Plugin Landing Page}}
\sectionsep

\end{minipage}
\end{document}
